A Dependently Typed Multi-Stage Calculus \ifnotanonymous\thanks{Supported by organization x.}\fi

### 2019-06-12 main.tex
[WIP] Review existing comments.

We assume the denumerable set of type variables, ranged over by
metavariables \(X, Y, Z\), the denumerable set of variables, ranged
over by \(x,y,z\), the denumerable set of constants, ranged over by
\(c\), and the denumerable set of stage variables, ranged over by
\(\alpha, \beta, \gamma\).  The metavariables \(A, B, C\) range over
sequences of stage variables; we write \(\varepsilon\) for the empty
sequence.  \AI{I prefer $\varepsilon$ for the nonempty sequence.}  \LMD is defined by the following grammar:

@@

@@

A kind, which is used to classify types, is either $*$, the kind of
proper types (types that terms inhabit), or $\Pi x\colon\tau.K$, the kind
of type operators that takes $x$ as an argument of type $\tau$ and returns a type
of kind $K$.
% Types
% of terms have kind $*$ and dependent types have $\Pi$-kinds.  For
% example, $\lambda x:\I.x$ has type $\Pi x:\I.\I$, which has $*$ kind.
% \red{この段落は短いので型の段落と結合するか?}
% Types
A type is a type variable $X$, which is declared in the signature with its kind, a dependent function type $\Pi x:\tau_1.\tau_2$,
an application of a type (operator) of $\Pi$-kind to a term, a code type $\TW_\alpha$, or an $\alpha$-closed type $\F\alpha.\tau$.
We sometimes abbreviate $\Pi x:\tau_1.\tau_2$ to $\tau_1 \rightarrow \tau_2$ if
$x$ is not a free variable in $\tau_2$. \AI{This should be mentioned after free variables are introduced.}
An application of a term to a dependent function type \AI{this sounds like $M\, (\Pi x:\tau_1.\tau_2)$} is, for example, $\text{Vector}\ 10$
if type variable $\text{Vector}$ has the kind $\Pi x:\I.*$.
A code type $\TW_\alpha \tau$ denotes a code fragment of a term of type $\tau$.
An $\alpha$-closed type corresponds to a runnable code fragment.
Type constructors tie strongly \AI{Is ``tie strongly'' standard?} in the order of 
an application of a term to a dependent function type $\tau\ M$,
a code type $\TW_{\alpha} \tau$,
a dependent function type $\Pi x:\tau.\tau$, 
an $\alpha$-closed type $\F\alpha.\tau$.
Therefore, $\F\alpha.\TW_{\alpha}.\Pi x:\I.\text{Vector}\ 5$ is interpreted as
$\F\alpha.(\TW_{\alpha}.(\Pi x:\I.(\text{Vector}\ 5)))$. \AI{I don't understand this rule...}

@@

We adopt a \LLF-like system, where constants and type variables for base types \AI{``for base types''?} are given in the signature $\Sigma$, which 
are a sequence of declarations of the form $c:\tau$ and $X:K$.
For example, when we use integers in \LMD, $\Sigma = \I :: *, 1:\I, 2:\I, \cdots$.  \AI{It sounds like we need an infinite signature...}

@@

\AI{Since we always substitute $\varepsilon$ for stage variables, we may want to introduce a special notation, something like $\textit{erase}_\alpha(M)$.}

>>>>

\AI{Rename ``type variables'' to ``type-level constants''. }
We assume the denumerable set of type variables, ranged over by
metavariables \(X, Y, Z\), the denumerable set of variables, ranged
over by \(x,y,z\), the denumerable set of constants, ranged over by
\(c\), and the denumerable set of stage variables, ranged over by
\(\alpha, \beta, \gamma\).  The metavariables \(A, B, C\) range over
sequences of stage variables; we write \(\varepsilon\) for the empty
sequence.  \AI{I prefer $\varepsilon$ for the nonempty sequence.}  \LMD is defined by the following grammar:

@@

\AI{Add $M\,\alpha$ to terms.}

@@

A kind, which is used to classify types, is either $*$, the kind of
proper types (types that terms inhabit), or $\Pi x\colon\tau.K$, the kind
of type operators that takes $x$ as an argument of type $\tau$ and returns a type
of kind $K$.
% Types
% of terms have kind $*$ and dependent types have $\Pi$-kinds.  For
% example, $\lambda x:\I.x$ has type $\Pi x:\I.\I$, which has $*$ kind.
% \red{この段落は短いので型の段落と結合するか?}
% Types
A type is a type variable $X$, which is declared in the signature with its kind, a dependent function type $\Pi x:\tau_1.\tau_2$,
an application of a type (operator) of $\Pi$-kind to a term, a code type $\TW_\alpha$, or an $\alpha$-closed type $\F\alpha.\tau$.
We sometimes abbreviate $\Pi x:\tau_1.\tau_2$ to $\tau_1 \rightarrow \tau_2$ if
$x$ is not a free variable in $\tau_2$. \AI{This should be mentioned after free variables are introduced.}
An application of a term to a dependent function type \AI{this sounds like $M\, (\Pi x:\tau_1.\tau_2)$} is, for example, $\text{Vector}\ 10$
if type variable $\text{Vector}$ has the kind $\Pi x:\I.*$.
A code type $\TW_\alpha \tau$ denotes a code fragment of a term of type $\tau$.
An $\alpha$-closed type corresponds to a runnable code fragment.
Type constructors tie strongly \AI{Is ``tie strongly'' standard?} in the order of 
an application of a term to a dependent function type $\tau\ M$,
a code type $\TW_{\alpha} \tau$,
a dependent function type $\Pi x:\tau.\tau$, 
an $\alpha$-closed type $\F\alpha.\tau$.
Therefore, $\F\alpha.\TW_{\alpha} \Pi x:\I.\text{Vector}\ 5$ is interpreted as
$\F\alpha.(\TW_{\alpha} (\Pi x:\I.(\text{Vector}\ 5)))$. \AI{I don't understand this rule...}

@@

We adopt a \LLF-like system, where constants and type variables for base types \AI{``for base types''?} are given in the signature $\Sigma$, which 
are a sequence of declarations of the form $c:\tau$ and $X:K$.
For example, when we use integers in \LMD, $\Sigma = \I :: *, 1:\I, 2:\I, \cdots$.  \AI{It sounds like we need an infinite signature...}
\AI{Change Int to Bool.}

@@

\AI{Since we always substitute $\varepsilon$ for stage variables, we may want to introduce a special notation, something like $\textit{erase}_\alpha(M)$.}
\AI{We will use $[\alpha \mapsto \varepsilon]$ and $[\alpha \mapsto \beta]$.  The latter is renaming, so we can omit the definition.}
